Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-24 manuscript/manuscript.tex
Minor changes in manuscript

In order to test the accuracy of the GLQ approximation, \citet{Uieda2016} and \citet{Grombein2013} have compared the numerical model with the analytical solution of the gravity fields generated by a spherical shell with homogeneous density, the exceptional case with analytical solution \citep{Mikuska2006,Grombein2013}.

In case of variable density tesseroids, the comparison must obviously be made with a variable density spherical shell, whose analytical solution will depend on the chosen density function.
Because the literature has not offered it yet, we needed to develop it ourselves. \todo{ no se si ponerlo asi}

>>>>

The integrals that define the gravity fields in equations \ref{eq:tesseroid-pot}-\ref{eq:tesseroid-tensor} have analytical solutions for the exceptional case of a spherical shell with homogeneous density \citep{Mikuska2006,Grombein2013}.
\citet{Uieda2016} and \citet{Grombein2013} compared their numerical models (tesseroids with homogeneous density) with these analytical solutions in order to test the accuracy of their approximations.

In case of variable density tesseroids, the comparison must obviously be made with a variable density spherical shell, whose analytical solution will depend on the chosen density function.
Because the literature has not offered it yet, we had to develop it ourselves. \todo{ no se si ponerlo asi}
